Spin canonical divisors of log stacky curves

### 2015-07-01 stacky_write_up/spin_cring.tex
ACGH citation for petri's thm

\noindent
with multiplication structure corresponding to tensor product of
sections. In the case that $g \geq 2$, $\Omega_X$ is ample, so $X \cong \proj R$. When $g \geq 2$, Petri's
theorem gives generators and relations for $R(X, K_X)$ showing that
in most cases $R(X, K_X)$ is generated in degree 1 with relations
in degree 2 (one demonstration is given by Saint-Donat\cite[p. 157]
{saint-donat:proj}). This has the pleasant geometric consequence \todo{maybe use a different ref}
that all such canonically embedded curves are scheme theoretically 
cut out by quadratic equations.

>>>>

\noindent
with multiplication structure corresponding to tensor product of
sections. In the case that $g \geq 2$, $\Omega_X$ is ample, so $X
\cong \proj R$. When $g \geq 2$, Petri's theorem gives generators
and relations for $R(X, K_X)$ showing that in most cases $R(X, K_X)$
is generated in degree 1 with relations in degree 2
(demonstrations are given by Saint-Donat \cite[p. 157]
{saint-donat:proj} and Arbarello--Cornalba--Griffiths--Harris
\cite[Section 3.3]{acgh:algebraic-curves}). This has the pleasant 
geometric consequence that all such canonically embedded curves are 
scheme theoretically cut out by quadratic equations.
